\LARGE \bf Laser Tracker Placement Optimization for highly flexible manufacturing systems

### 2024-08-04 paper/paper.tex
added conclusion

\section{Sample Testcase}
To test the performance of our optimizer, we need to define a testcase.
Both robots are Comau NJ290 industrial robots with a reach of 2.9 meters.
The right robot services the CNC machine and the additive manufacturing system, while the left robot performs a high-precision manufacturing task.
For this test, the left robot follows a rectangular trajectory with dimensions of 0.4 meters in length and 0.6 meters in width, as depicted in Figure \ref{fig:trajectory}.
The aim is now to find a laser tracker and marker placement that can track the left robot throughout its entire trajectory.
We compare this to the performance of the initial population of marker and laser tracker placements used to start the optimization process.
Figure \ref{fig:iterations} illustrates the performance of the algorithm over multiple iterations.
The results show that the algorithm converges to a solution in roughly 40 iterations, which is relatively fast for an optimization approach.
This speed is likely due to the existence of numerous optimal placements for the laser tracker and markers.
The final solution is also depicted in Figure \ref{fig:trajectory}.

@@

>>>>

\section{Sample Testcase}
To test the performance of our optimizer, we need to define a testcase.
Both robots are Comau NJ290 industrial robots with a reach of 2.9 meters.
The right robot services the CNC machine and the additive manufacturing system, while the left robot performs a high-precision manufacturing task.
For this test, the left robot follows a rectangular trajectory with dimensions of 0.4 meters in length and 0.6 meters in width, as depicted in Figure \ref{fig:trajectory}.
The aim is now to find a laser tracker and marker placement that can track the left robot throughout its entire trajectory.
We compare this to the performance of the initial population of marker and laser tracker placements used to start the optimization process.
Figure \ref{fig:iterations} illustrates the performance of the algorithm over multiple iterations.
The results show that the algorithm converges to a solution in roughly 40 iterations, which is relatively fast for an optimization approach.
This speed is likely due to the existence of numerous optimal placements for the laser tracker and markers.
The final solution is also depicted in Figure \ref{fig:trajectory}.
In conclusion the results show that the optimization approach is capable of finding a suitable laser tracker and marker placement for the manufacturing system.
We have also verified that the algorithm is capable of handling the dynamic nature of the manufacturing system, as the optimization is performed over the entire trajectory of the robot.

@@

\section{Conclusion}

In this paper, we argue that automating the verification setup in manufacturing systems is feasible using optimization methods.
We demonstrated this with a particle swarm optimization algorithm that optimizes the placement of a laser tracker and markers. 
Although initially labor-intensive, this approach proves beneficial for frequently reconfiguring systems as it requires only a simulation for each verification. 
Our results confirm the algorithm's effectiveness in determining optimal sensor placements, significantly reducing the manual effort required by engineers. 
We believe sensor placement optimization is a promising tool for researchers to verify system performance. 
However, the field is nascent with several unanswered questions about integrating optimization in reconfiguration processes, 
the potential for setup reuse across different designs, and developing multiple optimal solutions. 
We hope this paper serves as a catalyst for further research in this domain.
